Performing Cluster Analysis on TAD boundaries & Annotations

### 2019-03-22 Scripts/evaluating_pca.Rmd
editted pca script

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
                       cl, resolution, predictortype, annotation,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
           data=data,
           #loadings = TRUE,
           label = TRUE, 
           label.size = 3,
           label.repel=T, 
           colour="Cluster",
           shape="Medoid",
           label.show.legend = FALSE) +
    theme_bw()
  dev.off()

@@

```{r}

>>>>

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
                       cl, resolution, predictortype, annotation,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  print({
    autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
           data=data,
           #loadings = TRUE,
           label = TRUE, 
           label.size = 3,
           label.repel=T, 
           colour="Cluster",
           shape="Medoid",
           label.show.legend = FALSE) +
    theme_bw()
  })
  dev.off()

@@

```{r}
pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "count", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "perc", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "10kb", predictortype = "dist", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "count", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "perc", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "25kb", predictortype = "dist", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "count", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "perc", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "50kb", predictortype = "dist", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "count", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "perc", annotation = "tfbs")

pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "chromstates")
pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "histones")
pcaplotfunction(cl = "K562", resolution = "100kb", predictortype = "dist", annotation = "tfbs")
